### 2021-07-22 ch/3-structure.tex
Just two items left!

The method is validated with experiments
on the UCI Adult Income dataset and the ProPublica/COMPAS dataset,
which have been mentioned several times in \chapref{ch:related-work},
and which are the most common tabular fairness datasets.
While both these datasets comprise only tabular data,
there is nothing in principle that stops this method from being used for other kinds of data.
The choice to use these datasets and not others
was predominantly made for easier comparison to baselines.

@@

\subsection{Publication 3}
\begin{refsection}[allreferences]
    \nocite{kehrenberg2020zeroshot}
    \printbibliography[heading=none]
\end{refsection}%
\noindent\textsc{Contributions:}
\begin{itemize}
  \item I developed the idea of distribution matching as an extension of the previous paper.
    In addition, I tried to achieve similar goals by applying clustering to an unlabelled auxiliary set,
    with supervision from the labelled training set.
    I wrote all of the initial implementation of the method, and a large part of the later refined implementation.
    I ran the majority of the experiments.
  \item V. Sharmanska developed the original link to a fairness problem
    and wrote parts of the introduction and related work and contributed to other sections.
  \item M. Bartlett introduced the idea of batches-of-bags.
    He also improved the \ac{NN} architectures of the encoder and the discriminator,
    ran experiments, wrote the sections on architecture and contributed to other parts of the paper.
  \item N. Quadrianto suggested how to combine the two research directions that I had into a coherent whole.
    He also gave general feedback and suggested directions to explore.
\end{itemize}

>>>>

The requirements for the model are that it outputs probabilities
and that they are well-calibrated --
which means that for those samples
that the model predicts a 10\% chance of having a positive label (\(y=1\))
about 10\% in fact have a positive label,
and analogously for all other predicted probabilities.
The probabilities are needed for calculating the expected target label,
and the calibration ensures that this expectation is sensible.
Thus, we picked a \acf{GP} model as one model for the experiments,
as they have a reputation for being well-calibrated.
However, they come with the downside that they are (at least in their standard form)
not well-suited to very high dimensional data like images.
As such, we also construct a model based on \acf{LR}.

The method is validated with experiments
on the UCI Adult Income dataset and the ProPublica/COMPAS dataset,
which have been mentioned several times in \chapref{ch:related-work},
and which are the most common tabular fairness datasets.
While both these datasets comprise only tabular data,
there is nothing in principle that stops this method from being used for other kinds of data.
The choice to use these datasets and not others
was predominantly made for easier comparison to baselines,
and shorter experiment runtime.

@@

\subsection{Publication 3 (work in progress)}
\begin{refsection}[allreferences]
    \nocite{kehrenberg2020zeroshot}
    \printbibliography[heading=none]
\end{refsection}%
\noindent\textsc{Contributions:}
\begin{itemize}
  \item I developed the idea of distribution matching as an extension of the previous paper.
    In addition, I tried to achieve similar goals by applying clustering to an unlabelled auxiliary set,
    with supervision from the labelled training set.
    I wrote all of the initial implementation of the method, and a large part of the later refined implementation.
    I ran the majority of the experiments.
  \item V. Sharmanska developed the original link to a fairness problem
    and wrote parts of the introduction and related work and contributed to other sections.
  \item M. Bartlett introduced the idea of batches-of-bags.
    He also improved the \ac{NN} architectures of the encoder and the discriminator,
    ran experiments, wrote the sections on architecture and contributed to other parts of the paper.
  \item N. Quadrianto suggested how to combine the two research directions that I had into a coherent whole.
    He also gave general feedback and suggested directions to explore.
\end{itemize}

### 2021-07-22 paper3/paper3.tex
Just two items left!

%\icmltitle{Learning with Perfect Bags:\\
%Addressing Hidden Stratification with Zero Labelled Data}
\textsc{Authors}:\\
Thomas Kehrenberg$^1$, Viktoriia Sharmanska$^1$, Myles Bartlett$^1$, and Novi Quadrianto$^1$ \\
\textsc{Affiliations}:\\
$^1$ Predictive Analytics Lab (PAL), University of Sussex, Brighton, UK\\
\textsc{Conference}:\;\; Submitted to \textit{International Conference on Machine Learning} (ICML), 2021 \\
% \textsc{DOI}:\;\;10.3389/frai.2020.00033
\textsc{Note}:\;\; The appendix has been included as section~\ref{sec:zsf-appendix}.

@@

As mentioned in \secref{ssec:on-disentangled-representation-learning},
\citet{locatello2020weakly} learned to disentangle from non-i.i.d.\ pairs
which share at least one underlying factor.
In our scenario, constructing the pairs each out of one sample from the training set and one sample from the deployment set
would satisfy this requirement if we allow the `underlying factor' to be quite abstract
(see also the section below for a discussion of this).
However, constructing the pairs each out of two \emph{bags} instead of two samples
makes the analysis much clearer:
bags from the training and deployment set are constructed such
that they both have the same distribution of \(y\) values (a uniform distribution over \(y\)),
but they differ in the distribution of \(s\) values.

@@

Another take-away from our work concerns the general disentangling setup described in
\citet{locatello2020weakly}
-- \ie\ using pairs that share at least one underlying factor but also differ some.
For our work, we found it advantageous to do this pair matching not on the level of samples,
but on the level of bags (\ie, small, specially-sampled \emph{sets} of samples).
It is possible that other disentangling problems would benefit
from a similar switch in perspective
that identifies not the samples but some other structure
as the natural way to construct the pairs for the disentangling.

>>>>

%\icmltitle{Learning with Perfect Bags:\\
%Addressing Hidden Stratification with Zero Labelled Data}
\textsc{Authors}:\\
Thomas Kehrenberg$^1$, Viktoriia Sharmanska$^1$, Myles Bartlett$^1$, and Novi Quadrianto$^1$ \\
\textsc{Affiliations}:\\
$^1$ Predictive Analytics Lab (PAL), University of Sussex, Brighton, UK\\
% \textsc{Conference}:\;\; Submitted to \textit{International Conference on Machine Learning} (ICML), 2021 \\
% \textsc{DOI}:\;\;10.3389/frai.2020.00033
\textsc{Note}:\;\; The appendix has been included as section~\ref{sec:zsf-appendix}.

@@

As mentioned in \secref{ssec:on-disentangled-representation-learning},
\citet{locatello2020weakly} learned to disentangle from non-i.i.d.\ pairs
which share at least one underlying factor.
In our scenario, constructing the pairs each out of one sample from the training set and one sample from the deployment set
would satisfy this requirement if we allow the `underlying factor' to be quite abstract
(see also the section below for a discussion of this).
However, constructing the pairs each out of two \emph{bags} instead of two samples
makes the analysis much clearer:
bags from the training and deployment set are constructed such
that they both have the same distribution of \(y\) values (a uniform distribution over \(y\)),
but they differ in the distribution of \(s\) values.
Thus, the \emph{shared} factor is the one concerning the prediction target \(y\),
and the \emph{differing} factor is the one concerning \(s\).

@@

However, it is not really accurate to say that
we found a new ``fairness-based'' way to learn disentanglements.
Rather, it is the opposite way: we found a new disentanglement-based fairness method.
In order to achieve the goal of fairness,
we used building blocks (like adversarial training)
which happen to also be used in disentanglement learning.
And thus, it is not surprising that the method does in fact work by disentangling,
but it was just the choice of tools which would get the job done that produced this outcome.
The fairness aspect only acted as the motivator, and did not in itself contribute to the solution.

Another take-away from our work concerns the general disentangling setup described in
\citet{locatello2020weakly}
-- \ie\ using pairs that share at least one underlying factor but also differ in some.
For our work, we found it advantageous to do this pair matching not on the level of samples,
but on the level of bags (\ie, small, specially-sampled \emph{sets} of samples).
It is possible that other disentangling problems would benefit
from a similar switch in perspective
that identifies not the samples but some other structure
as the natural way to construct the pairs for the disentangling.
